### 2020-10-09 input/figaddA.tex
rework figure

\begin{tikzpicture}[scale=1]

@@

  \draw[fill=white] (0, 0) node{$\bm{a}$} +(-5, -5) rectangle +(5, 5);

>>>>

\begin{tikzpicture}[scale=0.87]

@@

  \newcommand\ADD{\alpha}

  \draw[->] (-\X + 5pt, 0 + 2pt ) -- (0 - 5pt, 0 + 2pt); %% a - b
  \draw[<-] (-\X + 5pt, 0 - 2pt ) -- (0 - 5pt, 0 - 2pt); %% b - a

  \draw[->] (0 +5pt, 0 - 2pt) -- (\X -5pt, 0 - 2pt); %% b - c
  \draw[<-] (0 +5pt, 0 + 2pt) -- (\X -5pt, 0 + 2pt); %% c - b

  \draw[->] (0 + 2pt, 0 - 5pt) -- (0 + 2pt, \Y + 5pt); %% b - d
  \draw[<-] (0 - 2pt, 0 - 5pt) -- (0 - 2pt, \Y + 5pt); %% d - b

  \draw[<-] (\X - 3pt, 0 - 5pt) -- (0 + 5pt, \Y + 3pt); %% d - c
  \draw[->] (\X + 3pt, 0 - 5pt) -- (0 + 5pt, \Y - 3pt); %% c - d

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above]{$\ADD_a^0$};
  \draw (\X, 5pt) node[above]{$\ADD_c^0$};
